---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![Travis-CI Build Status](https://travis-ci.org/carloscinelli/benford.analysis.svg?branch=master)](https://travis-ci.org/carloscinelli/benford.analysis)
[![Build status](https://ci.appveyor.com/api/projects/status/igyn1737s67jqqnb/branch/master?svg=true)](https://ci.appveyor.com/project/carloscinelli/benford-analysis/branch/master)
[![Coverage Status](https://img.shields.io/codecov/c/github/carloscinelli/benford.analysis/master.svg)](https://codecov.io/github/carloscinelli/benford.analysis?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/benford.analysis)](https://cran.r-project.org/package=benford.analysis) 
![](http://cranlogs.r-pkg.org/badges/benford.analysis)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/"
)
```

The Benford Analysis (`benford.analysis`) package provides tools that make it easier to validate data using Benford's Law. The main purpose of the package is to identify suspicious data that need further verification.

## CRAN

You can install the package from CRAN by running:

```{r, eval = FALSE}
install.packages("benford.analysis")
```


## How to install the development version from GitHub

To install the GitHub version you need to have the package `devtools` installed. Make sure to set the option `build_vignettes = TRUE` to compile the package vignette. 

```{r, eval = FALSE}
# install.packages("devtools") # run this to install the devtools package
devtools::install_github("carloscinelli/benford.analysis", build_vignettes = TRUE)
```

## Example usage

The `benford.analysis` package comes with 6 real datasets from Mark Nigrini's book [Benford's Law: Applications for Forensic Accounting, Auditing, and Fraud Detection](http://www.amazon.com/gp/product/B007KG9ZAI/ref=as_li_ss_tl?ie=UTF8&camp=1789&creative=390957&creativeASIN=B007KG9ZAI&linkCode=as2&tag=analreal-20).

Here we will give an example using 189.470 records from the corporate payments data. First we need to load the package and the data:

```{r}
library(benford.analysis) # loads package
data(corporate.payment) # loads data
```

Then to validade the data against Benford's law you simply use the function `benford` in the appropriate column:

```{r}
bfd.cp <- benford(corporate.payment$Amount)
```


The command above created an object of class "Benford" with the results for the analysis using the first two significant digits. You can choose a different number of digits changing the `number.of.digits` paramater. For more information and parameters see `?benford`:

Let's check the main plots of the analysis:

```{r}
plot(bfd.cp)
```

The original data is in blue and the expected frequency according to Benford's law is in red. For instance, in our example, the first plot shows that the data do have a tendency to follow Benford's law, but also that there is a clear discrepancy at 50.

You can print the main results of the analysis:

```{r}
bfd.cp
```

The print method first shows the general information of the analysis, like the name of the data used, the number of observations used and how many significant digits were analyzed.

After that you have the main statistics of the log mantissa of the data. If the data follows Benford's Law, the numbers should be close to:

Statistic| Value
---------|------
Mean| 0.5
Variance| 1/12 (0.08333…)
Ex. Kurtosis| -1.2
Skewness| 0


Printing also shows the 5 largest discrepancies. Notice that, as we had seen on the plot, the highest deviation is 50. These deviations are good candidates for closer inspections. It also shows the results of statistical tests like the Chi-squared test and the Mantissa Arc test.

The package provides some helper functions to further investigate the data. For example, you can easily extract the observations with the largest discrepancies by using the `getSuspects` function. 

```{r}
suspects <- getSuspects(bfd.cp, corporate.payment)
suspects
```

More information can be found on the help documentation and examples. The vignette will be ready soon.